---
title: "Stats R Lab Core Challenge: Linear Model & Prediction"
author: "Linfeng Zhou"
date: "Sunday, August 02, 2015"
output: pdf_document
---


## 1 Summary statistics
  Firstly, we load the data and using summary() function to obtain summary statistics. 
  
```{r,echo=FALSE}
library(ggplot2)
setwd("E:/Github Data/NYU-UCSL-2015/R Core Challenge")
dataset <- read.csv("2014-07 - Citi Bike trip data.csv", header=TRUE)
dataset = subset(dataset,dataset$birth.year != "\\N")


## def z-score function & calculate z-score
zscore <- function(citibike_data){
  tripduration.sd <- sd(citibike_data$tripduration)
  tripduration.mean <- mean(citibike_data$tripduration)
  z <- (citibike_data$tripduration-tripduration.mean)/tripduration.sd
  return(z)
}

z <- zscore(dataset)

## subset data
bikedata_origi <- dataset 
bikedata_clean  <- subset(dataset, z<2 & z>-2)

add_age <- function (dataset)
{
  a <- 2015-as.numeric(as.character(dataset$birth.year))
}

```

   The summary statistics of all data are:
```{r}
summary(bikedata_origi$tripduration)

```
   The summary statistics of clean data are:
```{r}
summary(bikedata_clean$tripduration)

```

## 2 Histogram and boxplot

```{r,echo=FALSE}
library(ggplot2)

ggplot(bikedata_origi,aes(x=tripduration)) + geom_histogram(binwidth=150,fill="white",colour="black")+ggtitle("tripduration of Original Data")

ggplot(bikedata_clean,aes(x=tripduration)) + geom_histogram(binwidth=100,fill="white",colour="black")+ggtitle("tripduration of Clean Data")

ggplot(bikedata_origi,aes(x=factor(usertype),y=tripduration)) + geom_boxplot(outlier.size=0.1,outlier.shape=0) +ggtitle("Boxplot for Original Data")

ggplot(bikedata_clean,aes(x=factor(usertype),y=tripduration)) + geom_boxplot(outlier.size=0.1,outlier.shape=0) +ggtitle("Boxplot for Clean Data")

```

## 3 Regression analysis 
```{r,echo=FALSE}
bikedata_origi$age <- add_age(bikedata_origi)
bikedata_clean$age <- add_age(bikedata_clean)

mean_age <- function (dataset) {
  trip_by_age <- with(dataset,split(tripduration,age))
  tripduration <- sapply(trip_by_age,mean)
  tripduration  <- data.frame(tripduration)
  age <- as.numeric(names(trip_by_age))
  data <- cbind(tripduration,age)
}

origidata <- mean_age (bikedata_origi)
cleandata <- mean_age (bikedata_clean)

fit1 <- lm (tripduration ~ age , origidata)
fit2 <- lm (tripduration ~ age , cleandata)

summary(fit1)
summary(fit2)
```

## 4 Compare the two models and comment on the following  
  
  - Which model is better?
   
     From the regression analysis' summary, we can see that the R-square of original dataset is larger than the dataset without outliers, therefore, we conclude that first model is better.
  
  - What is the effect of age in trip duration?
     
    As we can see the coefficients of regression models, the coefficient of age is positive, which means age has a positive effect in trip duration.
  
  - What is the effect of outliers in these models?
  
    The outliers increase coefficients of models not only on age parameters but also on intercept, which may cause overfitting .
  
   - From this analysis, what would you recommend Citi Bike in terms of a more equitable and socially responsible program for NYC and other cities around the world?  
    
     According to our model, most users are in short-distance driving. Therefore we can set more citi bike in order to fit people's need. 
      