---
title: "Hypothesis Testing"
author: "Linfeng Zhou"
date: "July 17, 2015"
output: html_document
---
```{r,echo=FALSE}
# loading data from .csv file:
setwd("/Users/luke/Documents/NYU-UCSL-2015//R Challenge2/")
cleandata <- read.csv("Citi+Bike+Clean+Data.csv",header=TRUE)
cleandata$tripduration<- cleandata$tripduration /60 

## statement 2
## Test the hypothesis that the Median for overtime is 2hrs long 
## with α=5% (overtime = 45mins or more).

subsetdata2<-subset(cleandata$tripduration,cleandata$tripduration>=45)

mean2 <- mean(subsetdata2)
ttest <-  t.test(subsetdata2-120)

```
## Question 1
   Statement #1: The majority of the trips are for short commutes lasting no more than 15min.
   
  - What should be your null hypothesis?
      The null hypothesis is: $$H_{0}: \mu\leq15min $$
  - What is a reasonable alternative?
      $$H_{1}: \mu>15min$$
  - What type I error test are your conducting?
      The type I error I am conducting is 0.05.
  - What is significant level in your test?
      The significant level in my test is 0.05.
      
## Question 2 
  Statement #2:  Citi Bike System wants to tackle bike rides incurring in overtime fees, particularly their interest is in rides lasting more than 45min.
  
  - Test the hypothesis that the Median for overtime is 2hrs long with α=5% (overtime = 45mins or more).  
  
     - Method I: t(student) test </br>
     According to requirement, the null hypothesis and alternative hypothesis are:
    $$H_{0}: \mu > 120min \Leftrightarrow H_{1}: \mu \leq 120 min$$
    $\mu$ is population mean, the sample mean is: $\overline{X}$=`r mean2`. Using pre-built ```t.test``` function, the details of t-test are following:
    ```{r}
    t.test(subsetdata2-120)
    ```
    P-value of t-test is `r  ttest$p.value` < 0.05, therefore we deny the null hypothesis.
    - Method II: Sign test </br>
    library(nortest)
    lillie.test(subsetdata2) 
    
    t-test  small sample 
            and from norm distribution 
            
    using lillie.test ...
    the result show that subsetdata2 don't fit on norm distribute
    in this case, t test may have some erroronce
    
    sign test   median rather than mean  
    not effected by distribution 
    the null hypothesis and alternative hypothesis are:
    
    
    the result of sign test is :
    pvalue 
    deny null hypothesis
    
## Quenstion 3 

