---
title: "Descriptive & Summary Statistics of NYC CitiBike"
author: "Linfeng Zhou    lz1335@nyu.edu"
output: pdf_document
---
##Question 1: Summary statistics table for January 2015 data
    Firstly, we load the data from local dataset and checking the size and dimensions of this file.
```{r}
setwd("E:/Code/NYU-UCSL-2015/R")
citibike_data<-read.csv("201501-citibike-tripdata.csv",header=TRUE)
dim(citibike_data)  
   
```
   
   After that, we exploring headers in the .csv file

```{r}
names(citibike_data)
```
    
    Now, it's time to analyze our mission. Qustion 1 ask us to provide summary statistics tables for 
    
    - (1) all January 2015 data 
    
    - (2) January 2015 data without outliers
    
    It this situation, we should use z-scores and subset funtion to generate two dataset: first one 
    is the original one, and the second one is clean data (which don't have outliers). Using z-scores(Z>3)
    ,we can detect outliers from our original data and delete them.
    
```{r}
#COMPUTING Z-SCORE
tripduration.sd <- sd(citibike_data$tripduration)
tripduration.mean <- mean(citibike_data$tripduration)
z <- (citibike_data$tripduration-tripduration.mean)/tripduration.sd
```

    We have tow dataset:one is named, another is named. Using pre-bulit function we calculate the summary
    statistics for January 2015 data.(The code is omitted, but you can see it at Rmd file)

```{r, echo=FALSE}
#creating subsets of data by Z value (z>3 as outlier)
bikedata_clean <- subset(citibike_data, z<3)
bikedata_origi <- subset(citibike_data)


## calculating the count for tripduration 
bikedata_clean.count <- dim(bikedata_clean)[1]
bikedata_origi.count <- dim(bikedata_origi)[1]

## calculating the mean for tripduration 
bikedata_clean.mean <- mean(bikedata_clean$tripduration)
bikedata_origi.mean <- mean(bikedata_origi$tripduration)

## calculating the standard deviation for tripduration
bikedata_clean.sd <- sd(bikedata_clean$tripduration)
bikedata_origi.sd <- sd(bikedata_origi$tripduration)

## calculating the min for tripduration
bikedata_clean.min <- min(bikedata_clean$tripduration)
bikedata_origi.min <- min(bikedata_origi$tripduration)

## calculating the max for tripduration
bikedata_clean.max <- max(bikedata_clean$tripduration)
bikedata_origi.max <- max(bikedata_origi$tripduration)

## calculating the median for tripduration
bikedata_clean.median <- median(bikedata_clean$tripduration)
bikedata_origi.median <- median(bikedata_origi$tripduration)

## calculate the quantiles for tripduration
bikedata_clean.quantile <- quantile(bikedata_clean$tripduration)
bikedata_origi.quantile<- quantile(bikedata_origi$tripduration)

## summary for tripduration
bikedata_clean.summary<-c(bikedata_clean.count,bikedata_clean.mean,
                          bikedata_clean.sd,bikedata_clean.min,
                          bikedata_clean.max,bikedata_clean.median,
                          bikedata_clean.quantile[2],
                          bikedata_clean.quantile[4])
bikedata_origi.summary<-c(bikedata_origi.count,bikedata_origi.mean,
                          bikedata_origi.sd,bikedata_origi.min,
                          bikedata_origi.max,bikedata_origi.median,
                          bikedata_origi.quantile[2],
                          bikedata_origi.quantile[4]
                          )
## data.frame the suumary
bikedata_summary <- data.frame(bikedata_origi.summary,bikedata_clean.summary)
row.names(bikedata_summary )<-(c("Count","Mean","Standard Deviation","Min",
                                 "Max","Median","25% Quantiles",
                                  "75 Quantiles"))
```
    After that, we have organize all statistics in one table, which is:
```{r}
bikedata_summary 
```
  
  Comment on the folloing question:
   
   - What can you say about the central tendency of this month?
     
     The average value and median in original data are (`r bikedata_origi.mean`,`r bikedata_origi.median`), and in data without outliers are (`r bikedata_clean.mean`,`r bikedata_clean.median` )
     
   - What can you say about the spread and dispersion of the data?
   
     The range and standard deviation in original data are(`r bikedata_origi.max-bikedata_origi.min`,`r bikedata_origi.sd`), and the same statistics in data without outliers are(`r bikedata_clean.max-bikedata_clean.min`,`r bikedata_clean.sd`)
     
   - What is the effect of outliers as per our summary statistics?
     
     As we can see the summary statistics table, effects of outliers are: 1. Raised the average of
     dataset, the average value of original data is bigger than clean data. 2. Raised the standard deviation
     of the dateset. Other statistics like Max Value, Quantiles Value get a corresponding rise.
    
## Question 2: Visualize the trip duration by user type
   
   Using ggplot2, plots of trip duration data by user type are :

```{r,echo=FALSE}
library(ggplot2)
#Visualize the trip duration by user type using clean
bikedata_Customer<- subset(bikedata_clean,usertype=="Customer")
bikedata_Customer<- subset(bikedata_clean,usertype=="Subscriber")

## histgram of tropduration by user type
ggplot(bikedata_clean,aes(x=tripduration)) + geom_histogram(fill="white",colour="black") + 
      facet_grid(usertype~., scales="free") + ggtitle("Trip Duration by User Type")

## boxplat of tropduration by user type
ggplot(bikedata_clean,aes(x=factor(usertype),y=tripduration)) + geom_boxplot(outlier.size=0.1,outlier.shape=0) +ggtitle("Boxplot for CitiBike")

```

    Comment on the following:
    
    - How does outliers affect histograms and/or box plots? 
      
      It will affect on widths of histograms and amount of outliers on boxplots.
    
    - What do you expect the histogram of this month would look like if you were to plot it with outliers
      
      Histograms may have a long tail, and box plots may show outliers if there are too many outliers.
